PragBat Analysis

### 2022-04-07 analysis/analysis.Rmd
add model based rli

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study1")

@@

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study2")

>>>>

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study1")

@@

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study2")
